A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2025-01-15 manuscript/main.tex
manuscript + Batches
manuscript Wed 15 Jan 2025 17:07:35 EST

\subsection{Implementation}
Python
Pennylane\cite{bergholm_pennylane_2022}
Pennylane Qiskit\cite{javadi-abhari_quantum_2024}
Pennylane Qulacs\cite{suzuki_qulacs_2021}
Qiskit\cite{javadi-abhari_quantum_2024}
SciPy Minimize \cite{virtanen_scipy_2020}
Scikit-learn\cite{pedregosa_scikit-learn_2011}

Simulated using FakeQuebecbackend
IBM Quebec

Error mitigation using
TREX \cite{van_den_berg_model-free_2022}

\subsection{Dataset}
We trained our models using three datasets: a function fitting dataset, consisting of a noisy linear, quadratic, and sine function, used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.

@@

>>>>

\subsection{Implementation}
We perform all simulation calculations using PennyLane\cite{bergholm_pennylane_2022}, either using Qulacs\cite{suzuki_qulacs_2021} for state vector calcualtions, while noisy calculations were performed using \textit{qiskit-aer} with the \textit{FakeQuebec} backend as implemented in the PennyLane-Qiskit plugin.\cite{javadi-abhari_quantum_2024}
We perform calculations in the \textit{ibm\_quebec} device using circuits implemented using Qiskit\cite{javadi-abhari_quantum_2024}, due to issues we initially faced with running experiments on the real device using the PennyLane-Qiskit plugin.
For the experiments using PennyLane,  we utilize the Simultaneous Perturbation Stochastic Approximation method (SPSA) as implemented in PennyLane, while for the experiments run on \textit{ibm\_quebec} utilizes the Constrained Optimization By Linear Approximation (COBYLA) optimizer as implemented ing SciPy\cite{virtanen_scipy_2020}.
Each optimizer was chosen based on the performance for the given task.
All features ($\mathbf{x}$) and target values ($\mathbf{y}$) were scaled using the MinMaxScaler in Scikit-learn\cite{pedregosa_scikit-learn_2011}, such that all featues and target values are $\mathbb{R}\in [ -1,1 ]$.
For the simulations using \textit{FakeQuebec} and experiments on \textit{ibm\_quebec} we utilize Twirled Readout Error eXtinction (TREX) error mitigation.

\subsection{Dataset}
In this study, we explore three datasets: a function fitting dataset, consisting of a noisy linear, quadratic, and sine function, used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.

The noisy function fitting dataset is generated by

$f(x) = x + \varepsilon$ such that $\varepsilon \in \mathcal{N} (0, \sigma^{2} )$

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\linewidth]{../images/BSE/fivequbit/BSE5_learning_curves}
	\caption{}
	\label{fig:bse5learningcurves}
\end{figure}
